---
title: "Impute evaluation vignette"
output: html_document
---
## Package install and data import

```{r message=FALSE}
library(magrittr)
library(knitr)
library(ggplot2)
library(reshape2)
source('Imputation evaluations.R')
data_test <- read.csv('OB_data/Ob_met_nona.csv', row.names = 1)
group <- rownames(data_test) %>% gsub('()-.*', '\\1', .) %>% as.factor()
```

```{r echo=FALSE}
kable(head(data_test[, 1:8]), format = 'markdown')
print(group)
```

# MCAR
## MCAR generation and imputation
```{r}
MCAR_list <- MCAR_gen_imp(data_c = data_test, prop = seq(.1, .5, .1), impute_list = c('kNN_wrapper', 'SVD_wrapper', 'Mean_wrapper', 'Median_wrapper', 'RF_wrapper'), cores = 10)
```

## MCAR NRMSE evaluation and plot
```{r echo=TRUE}
MCAR_NRMSE_list <- NRMSE_cal_plot(MCAR_list, plot = T, x = 'Miss_Prop')
```

```{r echo=FALSE}
kable(head(MCAR_NRMSE_list$NRMSE))
cat('The above table shows the NRMSE of different imputaion methods')
kable(head(MCAR_NRMSE_list$NRMSE_melt))
cat('The above melted table is good for ggplot2')
```

## MCAR PCA Procrustes analysis and plot
```{r echo=TRUE}
MCAR_PCA_ProSS_list <- Procrustes_cal_plot(MCAR_list, DR = 'PCA', nPCs = 2, x = 'Miss_Prop', plot = T)
```

```{r echo=FALSE}
kable(head(MCAR_PCA_ProSS_list$Pro_SS))
cat('The above table shows the Procrustes Sum of Squared Error of different imputaion methods')
kable(head(MCAR_PCA_ProSS_list$Pro_SS_melt))
cat('The above melted table is good for ggplot2')
```

## MCAR T-test results correlation
```{r echo=TRUE}
MCAR_Ttest_cor_list <- Ttest_cor_cal_plot(MCAR_list, group = group, plot = T, x = 'Miss_Prop', cor = 'P')
```
```{r echo=FALSE}
kable(head(MCAR_Ttest_cor_list$P_cor))
cat('The above table shows the Pearson Correlation of log T-test P-values between imputed data and complete data')
kable(head(MCAR_Ttest_cor_list$S_cor))
cat('The above table shows the Spearman Correlation of T-test P-values between imputed data and complete data')
```

## MCAR PLS Procrustes analysis and plot
```{r echo=TRUE}
MCAR_PLS_ProSS_list <- Procrustes_cal_plot(MCAR_list, DR = 'PLS', nPCs = 2, outcome = group, x = 'Miss_Prop', plot = T)
```

```{r echo=FALSE}
kable(head(MCAR_PLS_ProSS_list$Pro_SS))
cat('The above table shows the Procrustes Sum of Squared Error of different imputaion methods')
kable(head(MCAR_PLS_ProSS_list$Pro_SS_melt))
cat('The above melted table is good for ggplot2')
```

# MNAR
## MNAR generation and imputation
```{r}
MNAR_list <- MNAR_gen_imp(data_c = data_test, mis_var_prop = seq(.1, .8, .1), var_mis_prop = seq(.1, .6, .01), impute_list = c('kNN_wrapper', 'SVD_wrapper', 'QRILC_wrapper', 'HM_wrapper', 'Zero_wrapper'), cores = 5)
```

## MNAR NRMSE evaluation and plot
```{r echo=TRUE}
MNAR_NRMSE_list <- NRMSE_cal_plot(MNAR_list, plot = T, x = 'Miss_Prop')
```

```{r echo=FALSE}
kable(head(MNAR_NRMSE_list$NRMSE))
cat('The above table shows the NRMSE of different imputaion methods')
kable(head(MNAR_NRMSE_list$NRMSE_melt))
cat('The above melted table is good for ggplot2')
```

## MNAR NRMSE rank evaluation and plot
```{r echo=TRUE}
MNAR_NRMSE_rank_list <- NRMSE_rank_cal_plot(MNAR_list, plot = T, x = 'Miss_Num')
```

```{r echo=FALSE}
kable(head(MNAR_NRMSE_rank_list$NRMSE_rank))
cat('The above table shows the NRMSE ranks of different imputaion methods')
kable(head(MNAR_NRMSE_rank_list$NRMSE_rank_melt))
cat('The above melted table is good for ggplot2')
```

## MNAR PCA Procrustes analysis and plot
```{r echo=TRUE}
MNAR_PCA_ProSS_list <- Procrustes_cal_plot(MNAR_list, DR = 'PCA', nPCs = 2, x = 'Miss_Num', plot = T)
```

```{r echo=FALSE}
kable(head(MNAR_PCA_ProSS_list$Pro_SS))
cat('The above table shows the Procrustes Sum of Squared Error of different imputaion methods')
kable(head(MNAR_PCA_ProSS_list$Pro_SS_melt))
cat('The above melted table is good for ggplot2')
```

## MNAR T-test results correlation
```{r echo=TRUE}
MNAR_Ttest_cor_list <- Ttest_cor_cal_plot(MNAR_list, group = group, plot = T, x = 'Miss_Num', cor = 'P')
```
```{r echo=FALSE}
kable(head(MNAR_Ttest_cor_list$P_cor))
cat('The above table shows the Pearson Correlation of log T-test P-values between imputed data and complete data')
kable(head(MNAR_Ttest_cor_list$S_cor))
cat('The above table shows the Spearman Correlation of T-test P-values between imputed data and complete data')
```

## MNAR PLS Procrustes analysis and plot
```{r echo=TRUE}
MNAR_PLS_ProSS_list <- Procrustes_cal_plot(MNAR_list, DR = 'PLS', nPCs = 2, outcome = group, x = 'Miss_Num', plot = T)
```

```{r echo=FALSE}
kable(head(MNAR_PLS_ProSS_list$Pro_SS))
cat('The above table shows the Procrustes Sum of Squared Error of different imputaion methods')
kable(head(MNAR_PLS_ProSS_list$Pro_SS_melt))
cat('The above melted table is good for ggplot2')
```

